\documentclass{coverletter}
\usepackage{fontawesome5}

\begin{document}

% ─────────────────────────────────────────────────────────────────────────────
%  HEADER — Name + Contact Icons
% ─────────────────────────────────────────────────────────────────────────────
\begin{center}
  {\Large\sffamily\bfseries\color{namecolor} Yuanshuo Du}\\[0.14cm]
  % Row 1: GitHub · LinkedIn · Email (with icons)
  {\sffamily\small
    \href{https://github.com/YuanshuoDu}{\color{accent}\faGithub\color{muted}\ YuanshuoDu}
    \quad\textbullet\quad
    \href{https://linkedin.com/in/yuanshuodu}{\color{accent}\faLinkedin\color{muted}\ yuanshuodu}
    \quad\textbullet\quad
    \href{https://mail.google.com/mail/?view=cm&to=duyuanshuo@gmail.com}{\color{accent}\faEnvelope\color{muted}\ duyuanshuo@gmail.com}
  }\\[0.07cm]
  % Row 2: Phone · Location (with icons)
  {\sffamily\small\color{muted}
    \href{tel:+353894546468}{\color{accent}\faPhone\color{muted}\ +353 89 454 6468}
    \quad\textbullet\quad
    \href{https://www.google.com/maps/place/Dublin,+Ireland}{\color{accent}\faMapMarker\color{muted}\ Dublin, Ireland}
  }
\end{center}

\clrule

% ─────────────────────────────────────────────────────────────────────────────
%  OPENING — Metric-forward hook, ATS-safe
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\sffamily\small\color{primary}Dear Hiring Manager,}

\vspace{0.22cm}

\noindent%
{\sffamily\small\color{secondary}
  Across 12 departments and 5,000 users, I've seen what happens when security stays
  theoretical --- and what changes when someone makes it real. As an ISO 27001 Lead Auditor
  who closed a pharmaceutical certification with zero major non-conformities and drove a
  \textbf{40\% year-on-year drop in phishing incidents} at YumChina, I bring both the
  auditor's rigour and the attacker's creativity to every control I design.}

\vspace{0.30cm}

% ─────────────────────────────────────────────────────────────────────────────
%  TAGLINE BLOCK — Full-width, high-impact, visually distinct with border
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
\begingroup
  \setlength{\fboxrule}{0.8pt}%
  \setlength{\fboxsep}{0pt}%
  \fcolorbox{accent}{accent!6}{%
    \parbox{\linewidth}{%
      \vspace{0.32cm}%
      \hspace{0.70cm}%
      \begin{minipage}{\dimexpr\linewidth-1.4cm}
        {\sffamily\bfseries\LARGE\color{primary}
          Compliant by design. Resilient by default.}
        \vspace{0.18cm}
        {\sffamily\small\color{secondary}
          \faShieldHalved\ ISO 27001 Lead Auditor\quad
          \faCertificate\ GDPR Specialist\quad
          \faCheck\ KnowBe4 Security Awareness\quad
          \faCheck\ SIEM / Threat Modeling}
        \vspace{0.30cm}
      \end{minipage}%
    }%
  }%
\endgroup

\vspace{0.30cm}

% ─────────────────────────────────────────────────────────────────────────────
%  WHY THIS COMPANY — ATS-safe rewrite (no placeholders)
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\raggedright\sffamily\small\color{primary}
  \llap{\color{accent}\rule[0.12ex]{3pt}{1em}\hspace{0.35em}}\textbf{Why This Role and Organisation}}

\vspace{0.14cm}

\noindent%
{\raggedright\sffamily\small\color{secondary}
  I look for organisations that treat security as a design constraint, not a checkbox.
  That means teams who understand that ISO 27001 certification is a starting point,
  not a destination --- and who measure success in reduced incidents and real behavioural
  change, not paperwork. I've built compliance frameworks from the ground up, run
  SIEM-driven incident response, automated security workflows with AI, and worked inside
  engineering teams to make DevSecOps a practice rather than a promise. I want to do
  all of that somewhere it compounds.}

\vspace{0.30cm}

% ─────────────────────────────────────────────────────────────────────────────
%  WHAT I BRING — Accent-bullet list, ATS-safe plain bold, STAR structure
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\raggedright\sffamily\small\color{primary}
  \llap{\color{accent}\rule[0.12ex]{3pt}{1em}\hspace{0.35em}}\textbf{What I Bring to the Table}}

\vspace{0.16cm}

\begin{itemize}
  \setlist{noitemsep,topsep=0pt,partopsep=0pt,parsep=0pt}
  \setlist[itemize]{%
    leftmargin=1.3em,
    label=\color{accent}\textbullet,
    itemsep=0.16cm,
    parsep=0.06cm,
    before=\sffamily\small\color{secondary},
  }

  \item \textbf{40\% reduction in phishing incidents year-on-year across 5,000 users} ---
    Coordinated multi-cycle KnowBe4 phishing simulations for YumChina: designed campaigns,
    identified high-risk segments, delivered targeted follow-up training, and integrated
    completion tracking with Azure AD role-based access reviews; click-through rates dropped
    \textbf{25\%} and reporting rates rose \textbf{80\%}.

  \item \textbf{Zero major non-conformities at ISO 27001 certification across 12 departments} ---
    Authored the compliance documentation framework for a pharmaceutical client, aligned
    technical controls with business requirements, and led the internal audit process;
    certification achieved in 14 months; BCP/DR playbooks developed for all business-critical assets.

  \item \textbf{200+ employees trained across 3 international sites with 35\% improvement
    in post-training security scores} --- Delivered social engineering, GDPR, and incident
    reporting training for Decathlon and Splio (France); all content mapped to ISO 27001
    Annex A controls; phishing incidents dropped 40\% year-on-year post-training.

  \item \textbf{20+ critical and high vulnerabilities remediated pre-production} ---
    Conducted penetration testing using OWASP PTES and NIST frameworks; applied CVSS
    scoring, produced prioritised remediation reports, and presented findings to engineering
    leadership; zero high/critical findings remained at production release.

  \item \textbf{BCP/DR framework designed and tested annually across 12 departments} ---
    Conducted business impact analysis for a pharmaceutical client; developed business
    continuity and disaster recovery playbooks aligned with ISO 27001 Annex A controls;
    zero critical-system downtime recorded across two consecutive certification audit cycles.

  \item \textbf{Release cycles cut from 2 days to 15 minutes} ---
    Automated CI/CD pipelines in Kubernetes on Azure with SAST/DAST security gates baked
    into every commit; implemented SIEM log forwarding for production workloads; delivery
    velocity improved without compromising the security posture.

\end{itemize}

\vspace{0.30cm}

% ─────────────────────────────────────────────────────────────────────────────
%  SKILLS — Clean pill row, ATS keyword reinforcement
% ─────────────────────────────────────────────────────────────────────────────
\noindent%\begin{minipage}{\linewidth}
\sffamily\footnotesize\color{secondary}
  \skillpill{ISO 27001 Lead Auditor}\quad\skillpill{GDPR}\quad\skillpill{KnowBe4}\quad\skillpill{Penetration Testing}\quad\skillpill{OWASP Top 10}\quad\skillpill{CVSS}\\
  \skillpill{Security Awareness Training}\quad\skillpill{Social Engineering}\quad\skillpill{SIEM / Log Analysis}\quad\skillpill{Incident Response}\quad\skillpill{Zero Trust}\quad\skillpill{Python}\quad\skillpill{Linux}\quad\skillpill{Azure}\\
  \skillpill{Kubernetes}\quad\skillpill{GitHub Actions CI/CD}\quad\skillpill{DevSecOps}\quad\skillpill{Risk Assessment}\quad\skillpill{Compliance Documentation}\quad\skillpill{BCP / DR}\quad\skillpill{Vulnerability Management}\quad\skillpill{AI Automation}\quad\skillpill{Threat Modeling}
\end{minipage}

\vspace{0.30cm}

% ─────────────────────────────────────────────────────────────────────────────
%  CTA + SIGN-OFF
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\raggedright\sffamily\small\color{secondary}
  Based in Dublin, Ireland and available for immediate start, I respond to all serious
  inquiries within one business day. I'd welcome a conversation about how I could
  contribute to your team --- reach me at
  \href{https://mail.google.com/mail/?view=cm&to=duyuanshuo@gmail.com}{\color{accent}duyuanshuo@gmail.com}
  or +353 89 454 6468.}

\vspace{0.30cm}

\noindent%
{\sffamily\small\color{secondary}Warm regards,\par
\vspace{0.06cm}
{\sffamily\bfseries\Large\color{namecolor} Yuanshuo Du}\par
\vspace{0.04cm}
{\sffamily\small\color{muted} InfoSec Engineer \textbullet\ ISO 27001 Lead Auditor \textbullet\ Dublin, Ireland}

\end{document}
