\documentclass{simpleresume}

\begin{document}

% ── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  % Name — large, commanding, with subtle letter-spacing
  {\Large\sffamily\bfseries\color{primary}\kern0.04em Yuanshuo Du\kern0.04em}\\[0.42cm]
  % Contact row — muted, refined, with separators
  {\sffamily\small\color{muted}
    LinkedIn: \href{https://linkedin.com/in/yuanshuodu}{linkedin.com/in/yuanshuodu}
    \quad\textbullet\quad
    GitHub: \href{https://github.com/YuanshuoDu}{github.com/YuanshuoDu}
    \quad\textbullet\quad
    Mobile: +353 89 454 6468
    \quad\textbullet\quad
    \href{https://mail.google.com/mail/?view=cm&to=duyuanshuo@gmail.com}{duyuanshuo@gmail.com}
  }\\[0.15cm]
\end{center}

\headerrule

% ── Summary ───────────────────────────────────────────────────────────────────
\section{Summary}
\vspace{-0.5em}\hspace{0.55em}%
\begin{minipage}[t]{0.87\linewidth}
  \color{secondary}\small
  Full-stack Software Engineer with hands-on expertise in AI/ML, cloud architecture, and cybersecurity.
  Trained CNN models achieving 95\% accuracy for parking space detection. Remediated 20+ critical
  vulnerabilities in enterprise penetration testing projects. ISO 27001 compliance auditor with proven
  cross-cultural collaboration skills and Agile\slash Scrum experience.
  \color{muted}\normalsize
\end{minipage}\\[0.18cm]

% ── Skills ───────────────────────────────────────────────────────────────────
\section{Skills}
\noindent
\begin{tabular}[t]{@{}p{0.48\linewidth}p{0.48\linewidth}@{}}
\textbf{Languages}   & \textbf{Frameworks}                                          \\
{\sffamily\small\color{primary}
  \skillpill{Python}\ \skillpill{JavaScript}\ \skillpill{TypeScript}\ \skillpill{SQL}\ \skillpill{HTML/CSS}}
 & {\sffamily\small\color{primary}
  \skillpill{React}\ \skillpill{Node.js}\ \skillpill{Express}\ \skillpill{Redux}\ \skillpill{FastAPI}\ \skillpill{Django}} \\[0.12cm]
\textbf{Cloud/DevOps} & \textbf{Databases}                                            \\
{\sffamily\small\color{primary}
  \skillpill{Azure}\ \skillpill{Kubernetes}\ \skillpill{Docker}\ \skillpill{Terraform}\ \skillpill{CI/CD}\ \skillpill{Unix/Linux}}
 & {\sffamily\small\color{primary}
  \skillpill{PostgreSQL}\ \skillpill{Redis}\ \skillpill{MongoDB}} \\[0.12cm]
\textbf{Security}     &                                                              \\
{\sffamily\small\color{primary}
  \skillpill{ISO 27001 Compliance}\ \skillpill{Penetration Testing}\ \skillpill{Cybersecurity}}
 &
\end{tabular}

% ── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\textbf{Information Cybersecurity Specialist}
  \hfill {\sffamily\scshape\small\color{secondary}InsightSec, Shanghai}\\
  {\itshape\color{secondary}Penetration Testing \& Compliance}
  \hfill {\sffamily\scshape\small\color{muted}Apr 2021 -- Dec 2022}
\vspace{-1.3mm}
\begin{itemize}
  \item Led penetration testing engagements, identifying and remediating 20+ critical vulnerabilities across enterprise systems, reducing client risk exposure by an average of 70\%
  \item Managed Agile\slash Scrum projects end-to-end, coordinating cross-functional teams to ensure on-time delivery within budget constraints
  \item Guided clients through ISO 27001 ISMS certification, achieving compliance for 5+ organizations across finance, healthcare, and technology sectors
\end{itemize}

\vspace{0.12cm}\nopagebreak\noindent\textcolor{rule}{\rule{\linewidth}{0.6pt}}\nopagebreak\vspace{0.12cm}
\textbf{Web Engineer}
  \hfill {\sffamily\scshape\small\color{secondary}Sheffield African Caribbean Community Association}\\
  {\itshape\color{secondary}Full-Stack Web Development}
  \hfill {\sffamily\scshape\small\color{muted}Sep 2019 -- Apr 2020}
\vspace{-1.3mm}
\begin{itemize}
  \item Developed and maintained association website from scratch using WordPress and Figma, implementing SEO optimization that improved organic search visibility by 40\%
  \item Designed and built responsive front-end features, improving mobile usability and reducing maintenance overhead by 30\%
\end{itemize}

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\textbf{MSc Computer Science}
  \hfill {\sffamily\scshape\small\color{secondary}Technological University Dublin} \\
  {\itshape\color{secondary}Advanced Software Development}
  \hfill {\sffamily\scshape\small\color{muted}Dec 2024}
  \hfill {\sffamily\scshape\small\color{muted}2:1 (Merit)}
\vspace{-0.8mm}
{\small\color{secondary}Coursework: Software Design, Advanced Databases, Systems Architectures,
  Web App Architectures, Secure Systems Development, Deep Learning}

\vspace{0.1cm}
\textbf{MSc Management (International Business)}
  \hfill {\sffamily\scshape\small\color{secondary}University of Sheffield} \\
  {\itshape\color{secondary}CMI Level 7 Award in Strategic Management and Leadership}
  \hfill {\sffamily\scshape\small\color{muted}Apr 2021}
\vspace{-0.8mm}
{\small\color{secondary}Coursework: Marketing, Accounting, Financial Management, Agile Project Management}

\vspace{0.1cm}
\textbf{BA English and American Studies}
  \hfill {\sffamily\scshape\small\color{secondary}University of Pannonia (Erasmus+)} \\
  {\itshape\color{secondary}Erasmus+ Scholarship Recipient}
  \hfill {\sffamily\scshape\small\color{muted}Jun 2018}
  \hfill {\sffamily\scshape\small\color{muted}GPA: 4.11\slash 5}

% ── Projects ──────────────────────────────────────────────────────────────────
\section{Projects}

\textbf{Smart Parking Space Detection (Magpie)}%
  \hfill {\sffamily\scshape\small\color{muted}Sep -- Dec 2024}\\[-0.5mm]
{\itshape\color{secondary}Contributor -- Next.js, Node.js, PostgreSQL, CNN, Kubernetes, CI/CD}
\vspace{-0.6mm}
Trained CNN models on satellite images for automated parking space detection, achieving 95\%
accuracy. Designed and deployed a scalable microservices architecture on Kubernetes with fully
automated CI/CD pipelines.

\vspace{0.1cm}\nopagebreak\noindent\textcolor{rule}{\rule{\linewidth}{0.5pt}}\nopagebreak\vspace{0.1cm}
\textbf{AI-Powered Q\&A Platform}%
  \hfill {\sffamily\scshape\small\color{muted}Mar -- Sep 2024}\\[-0.5mm]
{\itshape\color{secondary}Lead Developer -- H5, UniApp, GitBook}
\vspace{-0.6mm}
Led H5 responsive development and cross-platform mobile app design for an AI-driven knowledge
base. Conducted comprehensive testing and produced detailed engineering documentation.

\vspace{0.1cm}\nopagebreak\noindent\textcolor{rule}{\rule{\linewidth}{0.5pt}}\nopagebreak\vspace{0.1cm}
\textbf{Travel Planner (MERN Full Stack)}%
  \hfill {\sffamily\scshape\small\color{muted}Sep -- Dec 2023}\\[-0.5mm]
{\itshape\color{secondary}Full-Stack Developer -- React, MaterialUI, Redux, Node.js, Express, MongoDB}
\vspace{-0.6mm}
Built a full-stack MERN travel planning application with user authentication (JWT + Google OAuth),
pagination, search, and real-time commenting system.

% ── Certifications ───────────────────────────────────────────────────────────
\section{Certifications}

{\sffamily\small
  \skillpill{ISO 27001 Internal Auditor (BSI)}\ \skillpill{CMI Level 7 Strategic Management}\ \skillpill{Trained CISA}\ \skillpill{PRINCE2}
}

% ── Publications ─────────────────────────────────────────────────────────────
\section{Publications}

{\sffamily\small\color{secondary}
  Du, Y. et al. (2025). The Development of a GIS for Public Amenities in Urban Areas.
  \textit{EduLearn25}
}

\end{document}
