\cvsection{Education}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MSc Computer Science (Advanced Software Development)} % Degree
    {Technological University Dublin} % Institution
    {Dublin, Ireland} % Location
    {Dec. 2022 -- Dec. 2024}
    {
      \begin{cvitems}
        \item {Main courses: Software Design, Advanced Databases, Systems Architectures, Web Application Architectures, Secure Systems Development, Working with Data, Deep Learning, Programming Paradigms}
        \item {Result: 2:1}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MSc Management (International Business)} % Degree
    {University of Sheffield} % Institution
    {Sheffield, UK} % Location
    {Sep. 2019 -- Apr. 2021}
    {
      \begin{cvitems}
        \item {Main courses: Marketing, Accounting and Financial Management, Managing People in Organizations}
        \item {Agile Project Management Capabilities}
        \item {CMI Level 7 Award in Strategic Management and Leadership}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BA English and American Studies} % Degree
    {University of Pannonia} % Institution
    {Hungary} % Location
    {Sep. 2015 -- Jun. 2019}
    {
      \begin{cvitems}
        \item {Main courses: Business Communication, Event Management, British Literature, History and Linguistics}
        \item {GPA: 4.11/5}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Erasmus+ Exchange Scholarship} % Degree
    {The University of the Balearic Islands} % Institution
    {Palma, Spain} % Location
    {Sep. 2017 -- Jul. 2018}
    {
      \begin{cvitems}
        \item {Adaptability to new skills}
        \item {Bilingual and cross-disciplinary research and learning ability}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
