\cvsection{Projects}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Security Automation \& DevSecOps Pipeline} % Project name
    {} % Organization
    {} % Location
    {Sep. 2024 -- Dec. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and implemented end-to-end DevSecOps pipeline integrating SAST/DAST tools (SonarQube, OWASP ZAP)}
        \item {Automated security scanning in CI/CD using GitHub Actions and Azure DevOps; reduced vulnerabilities by 60\%}
        \item {Deployed container security monitoring with Docker Scout and Kubernetes security policies}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vulnerability Assessment \& Compliance Automation} % Project name
    {} % Organization
    {} % Location
    {Mar. 2024 -- Sep. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Conducted penetration testing and vulnerability assessments for enterprise clients}
        \item {Automated ISO 27001 compliance checks using Python and Ansible; reduced audit preparation time by 40\%}
        \item {Developed security runbooks and incident response playbooks}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Phishing Simulation \& Security Awareness Platform} % Project name
    {https://github.com/Stevendu666/Security-Awareness} % URL
    {} % Location
    {Sep. 2023 -- Dec. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Built KnowBe4 integration for automated phishing simulation campaigns}
        \item {Developed training modules and tracked employee security awareness metrics}
        \item {Reduced phishing click rates by 35\% through targeted training programs}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Security Monitoring Dashboard} % Project name
    {} % Organization
    {} % Location
    {Jun. 2020 -- Dec. 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Developed SIEM dashboard for real-time network security monitoring}
        \item {Integrated threat intelligence feeds and automated alert triage}
        \item {Collaborated with security team on incident response and forensics}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
