\documentclass{coverletter}
\usepackage{fontawesome5}

\begin{document}

% ─────────────────────────────────────────────────────────────────────────────
%  HEADER — Name + Contact Icons
% ─────────────────────────────────────────────────────────────────────────────
\begin{center}
  {\Large\sffamily\bfseries\color{namecolor} Yuanshuo Du}\\[0.12cm]
  % Row 1: GitHub · LinkedIn · Email (with icons)
  {\sffamily\small
    \href{https://github.com/YuanshuoDu}{\color{accent}\faGithub\color{muted}\ YuanshuoDu}
    \quad\textbullet\quad
    \href{https://linkedin.com/in/yuanshuodu}{\color{accent}\faLinkedin\color{muted}\ yuanshuodu}
    \quad\textbullet\quad
    \href{https://mail.google.com/mail/?view=cm&to=duyuanshuo@gmail.com}{\color{accent}\faEnvelope\color{muted}\ duyuanshuo@gmail.com}
  }\\[0.06cm]
  % Row 2: Phone · Location (with icons)
  {\sffamily\small\color{muted}
    \href{tel:+353894546468}{\color{accent}\faPhone\color{muted}\ +353 89 454 6468}
    \quad\textbullet\quad
    \href{https://www.google.com/maps/place/Dublin,+Ireland}{\color{accent}\faMapMarker\color{muted}\ Dublin, Ireland}
  }
\end{center}

\clrule

% ─────────────────────────────────────────────────────────────────────────────
%  OPENING — Security lens, credibility setup, credibility signal
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\color{secondary}\sffamily\small
  Dear Hiring Manager,
}

\vspace{0.25cm}

\noindent%
{\color{secondary}\sffamily\small
  Most engineers ship features. After three years working inside production systems
  as a penetration tester — breaking things on purpose so developers could fix them
  before adversaries did — I came back to engineering with a permanent reframe:
  \textit{``What could this system fail at, and how do I make that outcome impossible?''}
  That question now shapes every API I design, every pipeline I build, and every
  architecture decision I make. It's why I believe security and velocity aren't
  opposites — they're the same discipline applied at different points in time.
}

\vspace{0.3cm}

% ─────────────────────────────────────────────────────────────────────────────
%  TAGLINE BLOCK — Identity statement with credibility anchors
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
\begingroup
  \setlength{\fboxrule}{0pt}%
  \setlength{\fboxsep}{0pt}%
  \colorbox{accent!8}{%
    \parbox{\linewidth}{%
      \vspace{0.35cm}%
      \hspace{0.5cm}%
      \begin{minipage}{\dimexpr\linewidth-1cm}
        {\sffamily\bfseries\LARGE\color{accent!80!primary}
          I build systems that are fast to ship\\
          and hard to break.}
        \vspace{0.08cm}
        \vspace{0.15cm}
        {\sffamily\small\color{muted}
          \faCode\ Full-Stack Engineer\quad
          \faShieldHalved\ Penetration Tester\quad
          \faCertificate\ ISO 27001 Lead Auditor}
        \vspace{0.35cm}
      \end{minipage}%
    }%
  }%
\endgroup

\vspace{0.4cm}

% ─────────────────────────────────────────────────────────────────────────────
%  WHY THIS COMPANY — Three-signal framework for tailoring
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\raggedright\sffamily\small\color{secondary}
  \llap{\color{accent}\rule[0.12ex]{3pt}{1em}\hspace{0.35em}}\textbf{Why [Company Name]}
}

\vspace{0.05cm}

\noindent%
{\color{secondary}\sffamily\small
  [Company Name] moves fast and takes security seriously — not as a checklist,
  but as an architectural reflex. That combination is rare, and it's exactly the
  engineering culture I'm built for. Three signals drew me here:
  \textbf{(1)} your public engineering work
  {[}e.g., zero-trust blog post, open-source tooling, SRE post-mortems\textbf{]}
  shows a team that thinks in systems, not just features;
  \textbf{(2)} your hiring process
  {[}e.g., practical technical screen, take-home project, panel architecture review\textbf{]}
  tells me you evaluate for the skills the job actually requires;
  and \textbf{(3)} your product solves a problem I find genuinely interesting.
  I'm not looking for any engineering role — I'm looking for a team whose standards
  I'd be proud to meet and whose work I'd learn from.
}

\vspace{0.3cm}

% ─────────────────────────────────────────────────────────────────────────────
%  WHAT I BRING — Narrative bullets: situation → action → measurable outcome
%  Round 2 improvements: HR-validated bold metrics, mentorship outcome, CTA fix
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\raggedright\sffamily\small\color{secondary}
  \llap{\color{accent}\rule[0.12ex]{3pt}{1em}\hspace{0.35em}}\textbf{What I Bring to the Table}
}

\vspace{0.1cm}

\noindent%
{\color{secondary}\sffamily\small

  \textbf{Found and fixed two critical vulnerabilities before production — saving an estimated \textbf{€200k+}.}
  \textit{Background:} As an ISO 27001 auditor and penetration tester I assessed
  20+ client systems across finance, healthcare, and technology. Using OWASP Top 10
  threat modelling, SAST/DAST tooling, and CVSS-scored remediation reports, I
  identified two critical findings — an insecure deserialisation flaw and an
  over-privileged service account. Both were resolved pre-deployment. The result was
  not just a cleaner audit: it was \textbf{€200k+} in avoided incident response,
  regulatory fines, and reputational exposure.

  \vspace{0.12cm}

  \textbf{Rebuilt a broken deployment pipeline: \textbf{2-day manual releases} $\rightarrow$ \textbf{sub-15-minute continuous delivery}.}
  \textit{Problem:} Bi-weekly shipping, three manual approval gates per deploy, and a
  third of on-call escalations traceable to bad releases. \textit{What I did:}
  Designed and implemented a GitHub Actions pipeline with Docker containerisation,
  Kubernetes blue/green rollouts, and automated security gates — SAST scans,
  container image scanning, and secret detection baked into CI, not bolted on after.
  Mentored two junior engineers through the transition; both now independently manage
  production deployments. \textit{Outcome:} deploy frequency increased \textbf{10$\times$},
  on-call incidents from bad deploys dropped to near zero, and the team reclaimed
  two engineering days per week.

  \vspace{0.12cm}

  \textbf{Deployed ML to production: \textbf{95\% accuracy}, \textbf{60\% labour reduction}, running today.}
  \textit{Constraint:} 10,000 labelled satellite images, six-week window.
  \textit{Decision:} ResNet50 transfer learning — borrowing a pre-trained network's
  feature detectors and fine-tuning the final layers on a small target dataset.
  The right architectural call for the data reality, not the textbook ideal.
  Containerised the inference service, deployed it as a Kubernetes microservice,
  and built monitoring to catch model drift. The system replaced manual survey
  labour and has run in production ever since.

  \vspace{0.12cm}

  \textbf{Led end-to-end delivery of a full-stack product: \textbf{4.7/5 client satisfaction}, on time.}
  \textit{Scope:} React/TypeScript front-end, Python/FastAPI back-end, PostgreSQL
  data layer, Azure infrastructure — delivered in six weeks. My role was architecture
  and technical delivery: running requirements trade-off conversations,
  making the call on build-vs-buy for the auth layer, and ensuring the security review
  happened before go-live, not after. The \textbf{4.7/5} reflected scores across
  technical quality, communication, and commitment to agreed scope.
}

\vspace{0.3cm}

% ─────────────────────────────────────────────────────────────────────────────
%  SKILLS — DevSecOps-forward
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\color{secondary}\sffamily\small
  \skillpill{Python} \skillpill{TypeScript} \skillpill{React} \skillpill{Node.js}
  \skillpill{FastAPI} \skillpill{Kubernetes} \skillpill{Docker}
  \skillpill{PostgreSQL} \skillpill{Azure} \skillpill{GitHub Actions}
  \skillpill{Terraform} \skillpill{CI/CD} \skillpill{DevSecOps}
  \skillpill{ISO 27001} \skillpill{OWASP} \skillpill{Penetration Testing}
}

\vspace{0.3cm}

% ─────────────────────────────────────────────────────────────────────────────
%  CTA — Specific, grounded, low-friction close (HR-validated improvement)
% ─────────────────────────────────────────────────────────────────────────────
\noindent%
{\color{secondary}\sffamily\small
  I'm based in Dublin (IST, UTC+1), available for immediate start, and specifically
  interested in roles where engineering quality and security discipline are treated
  as design criteria, not afterthoughts. I respond to all serious inquiries within
  one business day.

  If this sounds like a two-way fit, I'd welcome the chance to discuss your team's
  next challenge — and specifically how my background in offensive security can
  make your engineering team measurably stronger. Reach me at
  \href{https://mail.google.com/mail/?view=cm&to=duyuanshuo@gmail.com}{\color{accent}duyuanshuo@gmail.com}
  or \href{tel:+353894546468}{\color{accent}+353 89 454 6468}.
}

\vspace{0.3cm}

\noindent%
{\color{secondary}\sffamily\small Warm regards,}\\[0.25cm]
{\sffamily\bfseries\Large\color{namecolor} Yuanshuo Du}\\[0.05cm]
{\sffamily\small\color{muted} Full-Stack Engineer · Security-First · Dublin, Ireland}

\end{document}
